Performance of two different ontological and data access methods

### 2014-07-08 cold2014/magnus.tex
typo
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@740 43ef1190-90fd-4dd7-a769-d0121f02b80e
smaller changes
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@741 43ef1190-90fd-4dd7-a769-d0121f02b80e

We shall compare them to find their strengths and
weaknesses. Each approach contains an ontology and has its own way of
representing data.  To make this comparison we have used data about
the same domain, data about car models and their component
constraints.  The first approach is a generic ontology. By generic it
means that it can be used to represent any product model with
component constraints. The second approach is a domain specific
ontology which as the name implies, is only applicable with one
particular domain. In this thesis that domain is about car models.

@@

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Note that the implementation is not
itself an important contribution, it is the evaluation that is the key
contribution. Today only Renault, of all the car manufacturers, has
opened their data using semantic technologies. Volkswagen had their
data published until the start of 2013, but unfortunately they
canceled their Semantic Web project and the data were removed.
Fortunately, their ontologies are still open for the community to
use. Eventually, we found Daimler very forthcoming, as they offered
data about their A- and B-class cars.  The Daimler data used a custom
XML-based format, so we lifted the data using a \textit{Python} script into the
ontologies developed by Martin Hepp and Volkswagen.

To be able to put large stress on the application, which again would
allow us to bring out key strengths and weaknesses of the two
different approaches, we chose to create an application where a user
choose several or all car options specifications. The application was
implemented using Apache Maven, Spring and Apache Tomcat as well as
Jena.

@@

The application present users with a web interface where they can
input values for any specification they might want to search
for. There the user can input values for the different specifications,
for instance fuel type or CO$_2$ emission. After a user is done
choosing specifications he can execute the actual car model
search. The application extracts the data from the form and comprises
it into another format that can easily be used later on. The next step
begins in the search module. Here it starts a thread for each possible
car model to execute each individual search. In the end the user is
presented with a set of valid models to choose from, which contain the
chosen specifications, e.g. the user have searched for a model with
diesel fuel, automatic transmission, four or more gears and a maximum
of six seats.

@@

\subsection{Running the experiments}
In this section we will present several experiments with different
amount of factors.  The objective is to find out how the ontologies
will perform in comparison and identifying which factors affect the
outcome of each experiment. We did the ontology alignment and
development of the application to prevent the loss of precision with
either ontology.

@@

For brevity, we will use abbreviations given in Figure~\ref{facandabbrev}.

>>>>

We shall compare them to find their strengths and
weaknesses. Each approach contains an ontology and has its own way of
representing data.  To make this comparison we have used data about
the same domain, data about car models and their component
constraints.  The first approach is a generic ontology. By generic we
mean that it can be used to represent any product model with
component constraints. The second approach is a domain specific
ontology which as the name implies, is only applicable with one
particular domain. In this thesis that domain is about car models.

@@

We set out to evaluate different approaches based on a real use case
where a user is seeking to buy a new car based on detailed data
published by car manufacturers. Note that the implementation is not
itself important, it is the evaluation that is the key
contribution. Today only Renault, of all the car manufacturers, has
opened their data using semantic technologies. Volkswagen had their
data published until the start of 2013, but unfortunately they
canceled their Semantic Web project and the data were removed.
Fortunately, their ontologies are still open for the community to
use. Eventually, we found Daimler very forthcoming, as they offered
data about their A- and B-class cars.  The Daimler data used a custom
XML-based format, so we lifted the data using a \textit{Python} script into the
ontologies developed by Martin Hepp and Volkswagen.

To be able to put a major stress on the application, which again would
allow us to bring out key strengths and weaknesses of the two
different approaches, we chose to create an application where a user
choose several or all car options specifications. The application was
implemented using Apache Maven, Spring and Apache Tomcat as well as
Jena.

@@

The application presents users with a web interface where they can
input values for any specification they might want to search
for. There, the user can input values for the different specifications,
for instance fuel type or CO$_2$ emission. After a user is done
choosing specifications he can execute the actual car model
search. The application extracts the data from the form and comprises
it into another format that can easily be used later on. The next step
begins in the search module. Here it starts a thread for each possible
car model to execute each individual search. In the end the user is
presented with a set of valid models to choose from, which contain the
chosen specifications, e.g. the user have searched for a model with
diesel fuel, automatic transmission, four or more gears and a maximum
of six seats.

@@

\subsection{Running the experiments}
In this section we will present several experiments with different
number of factors.  The objective is to find out how the ontologies
will perform in comparison and identifying which factors affect the
outcome of each experiment. We did the ontology alignment and
development of the application to prevent the loss of precision with
either ontology.

@@

For brevity, we will use abbreviations given in Table~\ref{facandabbrev}.
